---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  results = "hide",
  message = FALSE
)
```

# EPhysMethods R Package

<!-- badges: start -->
<!-- badges: end -->

The EPhysMethods package contains helper functions and methods frequently used with electrophysiological data (filters, outlier detection, Fourier transform)

## Installation

You can install the development version of EPhysMethods from [GitHub](https://github.com/) with:

``` {r installation}
if (!requireNamespace("remotes", quietly = TRUE)){
  install.packages("remotes")
}
remotes::install_github("moritzlindner/EPhysMethods")
```

Note that  `EPhysMethods` recommends the github-deposited R Package  `EPhysData`. Installation usually works automatically. Updating, however may fail. If this is the case, update manually using the following line of code:

``` {r Update EPhysData}
remotes::install_github("moritzlindner/EPhysData")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(EPhysMethods)
## fast Fourier transform
library(units)
signal<-sin((1:1000)/33)*sin((1:1000)/20)
plot(signal)
fft_result <- fastfourier(signal, samp.freq = as_units(1000,"Hz"))
plot(fft_result$freq[1:20],abs(fft_result$fur[1:20]))

## Get spectral power
require(EPhysData)
X<-makeExampleEPhysData()
ggEPhysData(X)
psd<-PSD(X)
ggEPhysData(psd)

## identify most dissimilar columns 
data <- matrix(data = c(1, 2, 3, 4, 5, 6, 7, 8, 9), ncol = 3)
rejected <- autoreject.by.distance(data, threshold = 1)

```

